Solent region: Test Maps

### 2021-08-10 LSOA Fuel poverty.Rmd
Changing title

# Mapping the Lower Layer Super Output Area (LSOA)

```{r Loading in boundary data for the LSOA}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
message ("Loading LSOA boundaries from file")
lsoa_sf_data <- sf::read_sf(inf)
head(lsoa_sf_data)
table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
```

@@

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Winchester LOSA Fuel Pov 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Southampton LSOA Fuel Pov 2012 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

>>>>

# Mapping the Lower Layer Super Output Area (LSOA)
```{r Loading in boundary data for the LSOA}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
message ("Loading LSOA boundaries from file")
lsoa_sf_data <- sf::read_sf(inf)
head(lsoa_sf_data)
table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
```

@@

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Winchester LOSA Fuel Pov 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Southampton LSOA Fuel Pov 2012 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
